\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}

### 2016-09-15 eg6-letters/NIM/main.tex
added the papers
editing the NIM paper

\documentclass[reprint, amsmath,amssymb, aps]{revtex4-1}

@@

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
\author{
\Large{R. Dupr\'e$^{[1][2]}$, M. Hattawy$^{[1][2]}$, ...} \\
\vspace{+5mm}
\normalsize $^{[1]}$Argonne National Laboratory, Argonne IL 60439, USA \\
\normalsize $^{[2]}$Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France \\
\vspace{+5mm}
}

@@

\begin{abstract}
To study coherent Deeply Virtual Compton Scattering (DVCS) and coherent production of mesons on $^4$He, it is necessary to insure that the target nuclei is left intact by the reaction. This experiment is carried on at the CEBAF Large Acceptance Spectrometer (CLAS) at Jefferson laboratory (JLab), which has been used for similar studies on proton targets, however it cannot track low energy $^4$He. We developed for an experiment in 2009 a Radial Time Projection Chamber (RTPC) based on Gas Electron Multipliers (GEMs). The detector was positioned directly around the gaseous target of the experiment, allowing a detection threshold of $~$??? MeV/c for $^4$He. We describe in this article the design of the RTPC, the methods we developed to calibrate it and finally its performances.
\end{abstract}

@@

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in the Hall-B of the TJNAF in Newport News, Virginia, USA. The spectrometer is measuring charged particles as well as photons. The accelerator of the TJNAF provides a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC mentioned in this article has been used during a three months experimental run in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec Prop). In these experiments, CLAS detects the high energy charged particles and the final real photon, for the latter the coverage has been extended using the optional inner calorimeter (ref).

>>>>

\documentclass[reprint, amsmath,amssymb, aps]{revtex4}

@@

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
\author{
\Large{R. Dupr\'e$^{1,2}$, N. Baltzell$^{1,3}$, K. Hafidi$^{1}$, M.  
Hattawy$^{1,2}$, S. Stepanyan$^{3}$} \\
\vspace{+5mm}
\normalsize $^{1}$ Argonne National Laboratory, Argonne IL 60439, USA \\
\normalsize $^{2}$ Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and 
Universit$\acute{e}$ Paris Sud, Orsay, France \\
\normalsize $^{3}$ Jefferson Laboratory, Newport News, VA 230606, USA.
}

@@

\vspace{+25mm}
\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He remains intact and recoils as a whole in the final state. 
This experiment has been carried out using CEBAF Large Acceptance Spectrometer 
(CLAS) at JLab. The CLAS spectrometer has been used for similar studies on 
proton targets, however it cannot track recoils with momenta less than 250 
MeV/c.  We developed for an experiment in 2009 a Radial Time Projection Chamber 
(RTPC) based on Gas Electron Multipliers (GEMs).  The detector was positioned 
directly around the gaseous target of the experiment, allowing a detection 
threshold of $~$???  MeV/c for $^4$He. We describe in this article the design 
of the RTPC, the methods we developed to calibrate it and finally its 
performances.
\end{abstract}

@@

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF) in 
Newport News, Virginia, USA. The spectrometer is measuring charged particles as 
well as photons. The accelerator of the TJNAF provides a high power electron 
beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC 
mentioned in this article has been used during a three months experimental run 
in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent 
on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton 
Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec 
Prop). In these experiments, CLAS detects the high energy charged particles and 
the final real photon, for the latter the coverage has been extended using the 
optional inner calorimeter (ref).
